% LaTeX file for resume 
% This file uses the resume document class (res.cls)
%Prepared by Jared Woolstenhulme, September 2012

\documentclass[margin]{res}  % the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{fontspec}
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[hidelinks]{hyperref} %This package allows hyperlinks to be included so that viewers can click to visit a web page or send an email.
\usepackage{changepage}

\defaultfontfeatures{Mapping=tex-text}
\setmainfont {Adobe Garamond Pro} % Main document font
\setsansfont {Gill Sans} % Used in the from address line above the to address


\begin{document} 

\name{Dustin R White\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{School of Economic Sciences \\ Washington State University \\ 215, Hulbert Hall \\ Pullman, WA 99164 \\
\href{http://www.dustinrwhite.com}{http://www.dustinrwhite.com}}
\address{ Updated: \today \\ Citizenship: United States \\ Languages: English, Portuguese, Spanish \\ 425.443.1880 \\ \href{mailto:dustin.r.white@wsu.edu}{dustin.r.white@wsu.edu} }

\begin{resume} 
\section{\line(1,0){475}} %creates a horizontal line below the header

\section{\textnormal{EDUCATION}} 
\textbf{Ph.D.} in Economics, Washington State University \hfill (expected) May 2016 \\
Dissertation: \emph{``The Hidden Costs of Decisions in Applied Microeconomics''}\\
Advisor: Benjamin Cowan

\textbf{B.A.} in Economics, Brigham Young University \hfill 2011

\section{\textnormal{RESEARCH INTERESTS}}
Primary: Health, Labor Economics \\
Secondary: Econometrics, Industrial Organization, Machine Learning

\section{\textnormal{PUBLICATIONS}}

``The Effects of Merit-Based Financial Aid on Drinking in College,'' {\it Journal of Health Economics}, \emph{Forthcoming} (with Ben Cowan).

``Musculoskeletal manifestations of Sanfilippo syndrome (mucopolysaccharidosis type III),'' {\it Journal of Pediatric Orthopaedics}, 31(5), 594-598, 2011.
 
\section{\textnormal{SUBMITTED}}
``Teaching Marginal Revenue Product Using \emph{Moneyball}'' (with Jadrian Wooten).

\section{\textnormal{WORKS IN PROGRESS}}

%\textbf{Job Market Paper:}\\
``College Alcohol Consumption and NCAA Tournament Participation: the Health Cost of March Madness'' (with Ben Cowan and Jadrian Wooten)

%\textbf{Other Papers:}\\
``Agency Theory and the Decision to Work from Home''

``Network Externalities and Friendly Neighbors: When Firms Choose to Invite Competition'' (with Ben Smith)

\section{\textnormal{TEACHING \\EXPERIENCE}}

EconS 321 - The Economics of Sports in America (Online) \hfill Fall 2015 \\
EconS 321 - The Economics of Sports in America \hfill Summer 2015 \\
EconS 321 - The Economics of Sports in America \hfill Spring 2015 \\
EconS 321 - The Economics of Sports in America (Online) \hfill Fall 2014 \\
EconS 321 - The Economics of Sports in America \hfill Summer 2014 \\[12pt]
EconS 101 - Principles of Microeconomics \hfill Spring 2014 \\[12pt]
Dare to Dream Academy - Moneyball and Decisions with Numbers \hfill Summer 2015 \\
Dare to Dream Academy - Moneyball and Decisions with Numbers \hfill Summer 2014 \\

%\section{\textnormal{GRANTS}}
%%If you have Grants that you applied for and recieved, list them here but it is not typical for grad students. If you do not then simply erase this section.
%\textbf{Name of Grant Program},   \hfill Year \\
%\textit{``Title of Grant Proposal''}\\
%(with List of co-PI's), Amount Funded: \$\$.
%
%\textbf{Name of Grant Program},   \hfill Year \\
%\textit{``Title of Grant Proposal''}\\
%(with List of co-PI's), Amount Funded: \$\$.


\section{\textnormal{SCHOLARSHIPS\\AND AWARDS}}
\textbf{William M. Blayney Scholarship}, Washington State University \hfill 2015 \\[12pt]
\textbf{Graduate and Professional Student Association Travel Grant},\\ Washington State University \hfill 2014 \\


\section{\textnormal{PRESENTATIONS}}

\textbf{Southern Economics Association Meetings 2015}\\
\emph{``Modeling the Decision to Work from Home''}
Session Title: (Labor Supply). New Orleans, LA. %\href{http://link.to.slides.if.available.com}{\tiny{[slides]}}

\textbf{WSU School of Economic Sciences Seminar Series 2015}\\
\emph{``College Alcohol Consumption and NCAA Tournament Participation: the Health Costs of March Madness''}. Pullman, WA. %\href{http://link.to.slides.if.available.com}{\tiny{[slides]}}

\textbf{Beeronomics Conference 2015}\\
\emph{``The Effects of Merit-Based Financial Aid on Drinking in College''}. Seattle, WA. %\href{http://link.to.slides.if.available.com}{\tiny{[slides]}}

\textbf{Beeronomics Conference 2015}\\
\emph{``College Alcohol Consumption and Intercollegiate Athletics''}. Seattle, WA. %\href{http://link.to.slides.if.available.com}{\tiny{[slides]}}

\textbf{SES Graduate Student Association Poster Competition 2015}\\
\emph{``College Alcohol Consumption and Intercollegiate Athletics''} (Poster). Pullman, WA. %\href{http://link.to.slides.if.available.com}{\tiny{[slides]}}

\textbf{Southern Economics Association Meetings 2014}\\
\emph{``College Alcohol Consumption and Intercollegiate Athletics''}
Session Title: (Collegiate Sports I). Atlanta, GA. %\href{http://link.to.slides.if.available.com}{\tiny{[slides]}}

\textbf{Southern Economics Association Meetings 2014}\\
\emph{``Teaching MRP using Moneyball and Hall of Famers''}
Session Title: (Teaching and Sports Economics I). Atlanta, GA. %\href{http://link.to.slides.if.available.com}{\tiny{[slides]}}


\section{\textnormal{OTHER EXPERIENCE}}

\textbf{Research Assistant}, WSU (Pullman, WA) \\
Benjamin Cowan \hfill Fall, Spring, 2012-13\\
R. Karina Gallardo \hfill Fall, 2013

\textbf{Research Assistant}, Seattle Children's Hospital (Seattle, WA) \\
Klane K White \hfill Summer, 2010



\section{\textnormal{LEADERSHIP\\ AND SERVICE}} 
  
\textbf{President}, School of Economic Sciences Graduate Student Association \hfill 2015-16\\
\textbf{Treasurer}, School of Economic Sciences Graduate Student Association \hfill 2014-15\\
\textbf{Treasurer}, School of Economic Sciences Graduate Student Association \hfill 2013-14\\

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
% The tabular environmnet lines things up a little nicer. In this case there are just two columns separated by the & symbol.
\section{\textnormal{SKILLS}}
   \begin{tabular}{l p{3in}}
       Computer: &  Python (pandas, sqlite, sklearn, statsmodels, scipy, numpy), R, SQL, Linux, Stata, \LaTeX \\[12pt]
        Languages: & English (native), Portuguese (fluent), Spanish (proficient)
 \end{tabular}
\\

% I include a list of references on a seperate page and try and put everything else on two full pages (perhaps 3 full pages)
\newpage
\section{\textnormal{REFERENCES}}
\begin{table}[ht] % I use minpages within a table environment to make two columns for my references
%Column 1
\begin{minipage}[t]{0.5\linewidth} % The 0.5 says to use half of the page. If I wanted three columns then I would change this to 0.33
\vspace{2em}
\href{http://people.ses.wsu.edu/Cowan/}{\underline{Benjamin Cowan}}\\
School of Economic Sciences\\
Washington State University\\
Pullman, WA 99164-6210 USA\\
\emph{office:} 509.335.2184\\
\emph{email:} \href{mailto:ben.cowan@wsu.edu}{ben.cowan@wsu.edu}\\

\href{http://people.ses.wsu.edu/Rosenman/}{\underline{Robby Rosenman}}\\
School of Economic Sciences\\
Washington State University\\
Pullman, WA 99164-6210 USA\\
\emph{office:} 509.335.1193\\
\emph{email:} \href{mailto:yamaka@wsu.edu}{yamaka@wsu.edu}
\end{minipage} % End Column 1 
\hspace{0.5cm} % Add some space between the columns
\begin{minipage}[t]{0.5\linewidth} % Column 2
\vspace{2em}
\href{http://people.ses.wsu.edu/Mandal/}{\underline{Bidisha Mandal}}\\
School of Economic Sciences\\
Washington State University\\
Pullman, WA 99164-6210 USA\\
\emph{office:} 509.335.7553\\
\emph{email:} \href{mailto:bmandal@wsu.edu}{bmandal@wsu.edu}\\

\href{http://people.ses.wsu.edu/McCracken/}{\underline{Vicki McCracken (Teaching Reference)}}\\
School of Economic Sciences\\
Washington State University\\
Pullman, WA 99164-6210 USA\\
\emph{office:} 509.335.4728\\
\emph{email:} \href{mailto:mccracke@wsu.edu}{mccracke@wsu.edu}\\


\end{minipage} % End Column 2
\end{table}


\end{resume} 
\vspace{5em}


\begin{adjustwidth}{-5em}{5em}
\begin{large}
\begin{center}

The Hidden Costs of Decisions in Applied Microeconomics \\
Dissertation Summary\\[2em]

\end{center}
\end{large}
\textit{Chapter 1: College Alcohol Consumption and NCAA Tournament Participation: the Health Cost of March Madness}\\

Using the Harvard School of Public Health College Alcohol Study (CAS), we examine the effect of the NCAA Tournament on the level of binge drinking across a nationally representative survey of American campuses. Colleges and universities across the United States continue to increase expenditure on intercollegiate athletics. A focus on athletics may augment visibility of the university to prospective students and thereby benefit the school. It may also have a negative effect on the current student body by influencing risky behavior related to intercollegiate athletics, especially the consumption of alcohol commonly associated with game day festivities. We find that participation in the NCAA Tournament is associated with a 28\% increase in binge drinking by male students at participating schools. These results suggest that in addition to enjoying the benefits of greater athletic success, universities should confront the culture of binge drinking on game days by seeking to reduce binge drinking during the tournament, particularly among male students.\\

\textit{Chapter 2: Agency Theory and the Decision to Work from Home}\\

Applying the principal-agent model to the wage penalties experienced by individuals working from home, I predict that wages will converge between home-workers and office-workers as monitoring costs fall over time. I also predict that wage variance will decline for home-workers as monitoring costs fall. The nature of working from home has changed quickly as improved communications technology has made it easier for workers to correspond quickly and efficiently from home. Using data from the American Community Survey and Census data, I find that the wage penalty for home-workers fell from around 30\% in 1980 to a wage premium of 1.5\% in 2013 using a selection model to account for potential selection bias. Additionally, I find that wage variance for home-workers fell from 75\% higher in 1980 to 8.5\% higher relative to office-workers in 2013. This strongly suggests that the principal-agent model is appropriate in explaining changes in the nature of working from home.\\[3em]

\textit{Chapter 3: Network Externalities and Friendly Neighbors: When Firms Choose to Invite Competition}\\

In this paper, we propose that under certain circumstances firms may instead choose to \emph{reduce} barriers to entry as a profit-maximizing mechanism so long as the firm is able to induce growth in demand that exceeds the growth in supply provided by new entrants to the market. Economic theory on the subject of barriers to entry focuses almost exclusively on firms working to preserve market power and economic profits. We model the conditions under which this effect may exist and predict that in some industries, an increase in the number of participating firms will induce enough growth in the industry to allow existing firms to increase profit by inducing other firms to enter the market. We show that firms can in fact reduce barriers to entry for competitors and experience increased profits. This model differs from the agglomeration literature by proposing that firms deliberately lower fixed costs for their competitors as a rational act, instead of simply existing in locations where fixed costs are reduced by concentration of firms.

\end{adjustwidth}
\end{document} 



